Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth

### 2021-08-22 manuscript/agujournaltemplate.tex
agu revision requires figures at the same folder level as the tex source
sync title with ms word

\title{Geometric models overestimate lake depth due to imperfect slope
measurement}

@@

\begin{figure}
\noindent\includegraphics[width=0.74\textwidth]{../figures/slope_diagram_new}
\caption{Diagram showing the relations between true (black) and proxy (orange) metrics of lake geometry. Geometric depth calculated via Equation \ref{eq1} requires a single distance and slope metric.}\label{fig1}
\end{figure}

@@

% TODO insert map
\begin{figure}
      \begin{center}\includegraphics[width=0.65\textwidth]{../figures/00_map_bathy-1}\end{center}
      \caption{Map of study lakes showing A) lake maximum depth measurements, B) cross-section shape class, and C) reservoir classification.}\label{fig2}
      \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/01_geometry_base-1}
  \end{center}
  \caption{Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance distance to lake center and B) nearshore land slope versus in-lake slope. A best-fit line and coefficient of determination is shown to illustrate representativeness.}\label{fig3}
\end{figure}

@@

\begin{table}[h]
  \caption{Model fit and predictive accuracy metrics (RMSE = root mean square error, $R^2$ = coefficient of determination, MAPE = mean absolute percent error) for all combinations of true (in-lake slope, distance to the deepest point of the lake) and proxy (nearshore land slope, distance to lake center) metrics.} \label{table1}
  \centering
  % scripts/05_depth_model.R
  % data/01_depth_model/depth_grid_metrics.rds
  % tables/02_model_metrics.Rmd
\begin{tabular}{lllll}
  \hline
  slope & distance & RMSE & $R^2$ & MAPE\\
  \hline
  true & true & - & - & -\\
  true & proxy & 4.4 m & 0.70 & 29 \%\\
  proxy & true & 6.6 m & 0.32 & 60 \%\\
  proxy & proxy & 6.4 m & 0.35 & 59 \%\\
  \hline
\end{tabular}
\end{table}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{../figures/02_depth_model_grid_resid-1}
  \end{center}
  \caption{Depth model residuals (residual  = observed - predicted) in meters by cross-section shape and reservoir class indicating overprediction of concave and reservoir lakes.}\label{fig4}
\end{figure}

>>>>

\title{Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth}

@@

\begin{figure}
      \noindent\includegraphics[width=0.74\textwidth]{slope_diagram_new}
      \caption{Diagram showing the relations between true (black) and proxy (orange) metrics of lake geometry. Geometric depth calculated via Equation \ref{eq1} requires a single distance and slope metric.}\label{fig1}
\end{figure}

@@

% TODO insert map
\begin{figure}
      \begin{center}\includegraphics[width=0.65\textwidth]{00_map_bathy-1}\end{center}
      \caption{Map of study lakes showing A) lake maximum depth measurements, B) cross-section shape class, and C) reservoir classification.}\label{fig2}
\end{figure}

@@

\begin{figure}
      \begin{center}
            \includegraphics[width=0.75\textwidth,keepaspectratio]{01_geometry_base-1}
      \end{center}
      \caption{Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance distance to lake center and B) nearshore land slope versus in-lake slope. A best-fit line and coefficient of determination is shown to illustrate representativeness.}\label{fig3}
\end{figure}

@@

\begin{table}[h]
      \caption{Model fit and predictive accuracy metrics (RMSE = root mean square error, $R^2$ = coefficient of determination, MAPE = mean absolute percent error) for all combinations of true (in-lake slope, distance to the deepest point of the lake) and proxy (nearshore land slope, distance to lake center) metrics.} \label{table1}
      \centering
      % scripts/05_depth_model.R
      % data/01_depth_model/depth_grid_metrics.rds
      % tables/02_model_metrics.Rmd
      \begin{tabular}{lllll}
            \hline
            slope & distance & RMSE  & $R^2$ & MAPE  \\
            \hline
            true  & true     & -     & -     & -     \\
            true  & proxy    & 4.4 m & 0.70  & 29 \% \\
            proxy & true     & 6.6 m & 0.32  & 60 \% \\
            proxy & proxy    & 6.4 m & 0.35  & 59 \% \\
            \hline
      \end{tabular}
\end{table}

\begin{figure}
      \begin{center}
            \includegraphics[width=\textwidth,keepaspectratio]{02_depth_model_grid_resid-1}
      \end{center}
      \caption{Depth model residuals (residual  = observed - predicted) in meters by cross-section shape and reservoir class indicating overprediction of concave and reservoir lakes.}\label{fig4}
\end{figure}
